### 2023-02-08 doc/manuscript/translocation.qmd
Minor additions to previously-added comments

<!--# Mark W: Pulling from the methods, we say: "Translocations of [putatively resistant] *R. sierrae* were conducted in Yosemite National Park (California, USA) as part of an effort to reestablish populations of this endangered species."  Could be a good starting sentence.  Also, as I am reading through the results, our sections do not elude to the Allie's section.  We should discuss how our sections can set-up Allie's section with a few well-chosen words throughout.  -->

@@

<!--# Mark W: Regarding the above paragraph, what evidence do we have of "tolerance"? Are Bd loads significantly reduced in populations compared to epizootic levels? Can we convincingly state that the likely mechanism is more consistent with resistance or tolerance?  I ask because it would be nice to just use one of these terms in the paper and not get caught up in any resistance vs. tolerance discussions with reviewers.  -->

@@

<!--# To help constrain the possible values of omega, add information about recruitment probability observed in the study populations? Because we don't have accurate counts of subadults, can we even provide rough estimate of recruitment probability?  Mark W here: This would be great. If we have even ballpark estimates of \omega it would be useful to inclue.-->

>>>>

<!--# Mark W: Pulling from the methods, we say: "Translocations of [putatively resistant] *R. sierrae* were conducted in Yosemite National Park (California, USA) as part of an effort to reestablish populations of this endangered species."  Could be a good starting sentence.  Also, as I am reading through the results, our sections do not allude to the Allie's section.  We should discuss how our sections can set-up Allie's section with a few well-chosen words throughout.  -->

@@

<!--# Mark W: Regarding the above paragraph, what evidence do we have of "tolerance"? Are Bd loads significantly reduced in populations compared to epizootic levels? Can we convincingly state that the likely mechanism is more consistent with resistance or tolerance?  I ask because it would be nice to just use one of these terms in the paper and not get caught up in any resistance vs. tolerance discussions with reviewers.  Roland: Have a look at this paragraph of Knapp et al. PeerJ 2022: https://peerj.com/articles/12712/#p-61. We argue that there is evidence for resistance and tolerance. -->

@@

<!--# To help constrain the possible values of omega, add information about recruitment probability observed in the study populations? Because we don't have accurate counts of subadults, can we even provide rough estimate of recruitment probability?  Mark W here: This would be great. If we have even ballpark estimates of \omega it would be useful to include.-->
